The Cluster Difference Imaging Photometric Survey (CDIPS). I. Method, Light Curves, and Planet Candidates from Sectors 6--8

### 2019-05-23 paper/ms.tex
paper: wrote some

\shortauthors{Bouma et al.}
\shorttitle{CDIPS I: Method \& Sector 6}

@@

\title{
  The Cluster Difference Imaging Photometric Survey (CDIPS).
  I. Method \& TESS Light Curves from Sector 6
}

@@

The exoplanet field is evolving.
At the beginning, Doppler spectroscopy by the Geneva and California groups
led to the first exoplanet detections (CITE: Mayor 95, Butler, Marcy).
Some of these planets transited (CITE: Henry, Charbonneau).
Despite the geometric rarity of transits, photometric monitoring can
be performed in parallel, while spectroscopy cannot.
This enabled thousands of planet detections with the Kepler spacecraft
(CITE: Borucki, Morton).
The abundance of planets from Kepler taught us about statistics
(CITE: Howard, Fressin, Petigura).
By nature of its design, Kepler left open two major avenues for
improvement: (i) brighter stars, (ii) rare weirdos.
TESS (CITE: Ricker), by nature of its small, wide-field cameras, and
nearly all-sky coverage, can capitalize on both.
TESS observes more stars than Kepler, for on average less time.
One class of rare weirdo to which TESS is sensitive is stars in
clusters.  For brevity, we use the term ``cluster'' to refer to open
clusters, moving groups, associations, and star-forming regions.
Each of the $\sim$1000 star clusters of the Milky Way is a gift to
astrophysics, providing a sample of stars that vary widely in mass
but all have approximately the same age and composition.

Cluster stars have been monitored photometrically from the ground
(CITE: Joel thesis, Cambridge group).
A few clusters, NAME1 and NAME2, were observed by Kepler in its prime
mission (CITE: Meibom).
And a few more, most notably X,Y, and Z, were observed in K2's
ecliptic mission (CITE).

@@

Yet, there are formidable obstacles to deriving precise photometry
from the {\it TESS} images because of the relatively poor angular
resolution.  Almost all of the clusters are within 10 degrees of the
Galactic plane (see Figure~1), where the problems with crowding and
complex backgrounds are so severe that the {\it TESS}\, Science Team
has neglected that portion of the sky in their planet simulations
\citep{Sullivan_et_al_2015}. Similarly, the {\it TESS}\, Candidate
Target List deprioritizes all objects within $15^\circ$ of the
galactic plane~\citep{stassun_TIC_2018}, which includes 90\% of all
star clusters.  The large pixel size and the high stellar surface
density will make aperture photometry unreliable.  Yet, aperture
photometry is the basis of the official {\it TESS} data reduction
pipeline and almost all reduction methods that have been applied to
{\it Kepler} and {\it K2} data.

We have begun to produce photometry from the TESS images.
In what follows, \S~\ref{sec:method} presents BLAH, and
\S~\ref{sec:results} describes BLAH BLAH.
\S~\ref{sec:discussion} discusses, and \S~\ref{sec:conclusion}
concludes.

@@

A major motivator for the CDIPS project is to increase the number of
cluster stars for which continuous photometric timeseries are
available, and thus facilitate studies of exoplanetary and stellar
processes across different times and stellar environments.

An essential aspect of the project is therefore to define a {\it
cluster star sample}, consisting of stars that are thought to be
members of clusters.

Performing a homogeneous membership determination for every known
cluster is beyond the scope of this work.  Instead, we collect various
cluster membership catalogs from the literature.  We then use them to
identify cluster members for which we have already made lightcurves
from the TESS images.  Our goal in selecting stars is completeness,
rather than precision.  If there has been a claim in the literature
that a star should be considered as a cluster member, we aim to
provide a lightcurve for that star.

Table~N describes the cluster membership catalogs we have used to
identify candidate cluster members.  Since our photometric reduction
is based on positions reported in {\it Gaia DR2}, each of our
lightcurve sources by default is associated with a Gaia identifier.
Correspondingly, the cluster membership determinations performed by
\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018} are the
easiest case for us to merge against our lightcurve database.
For the TESS Sectors 1--5 lightcurves produced in this study, this
yielded X and Y lightcurves respectively.

@@

\subsection{Open clusters (OCs)}
\label{subsec:oc}

@@

\citet{cantat-gaudin_gaia_2018} used an unsupervised membership
assignment algorithm to identify clusters in the three-dimensional
astrometric space of proper motion and parallax. They used {\it Gaia}
photometry and radial velocities to then verify the claimed
membership properties.  From their Table~2, we collect 401{,}448
cluster members, in 1229 clusters, down to a limiting magnitude of
$G=18$.

@@

\paragraph{Pre-{\it Gaia} OC memberships}
\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
\citep[][a combination of USNO-B1{.}0 and 2MASS
astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
\citep{skrutskie_tmass_2006} and reported the existence of 2859 open
clusters and stellar associations.
We selected their ``$1\sigma$'' members according to the
combined photometric, kinematic, and spatial criteria described by
\citet{kharchenko_global_2012}.  Then, to obtain {\it Gaia}-DR2 source
identifiers for the members, we performed a crossmatch for {\it
Gaia}-DR2 sources within 5 arcseconds of the listed positions.  As an
additional constraint, we used the 2MASS photometry to predict the
$G$-band magnitudes\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
online, \texttt{2019-03-29}, or \citet{carrasco_gaia_2016}}, and
required that the measured $G$-magnitude fall within 2 magnitudes of
the predicted $G$-magnitude.  If multiple neighbors matched the
position and magnitude constraints, we took the nearest spatial
neighbor as the match.  From 373{,}226 stars, this yielded a unique
best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
between two neighbors for 17{,}774 stars.

The second (non-{\it Gaia} derived) open cluster membership catalog we
used was the \citet{dias_proper_2014} catalog, which was based on
UCAC4 proper motions.
From their 1805 reported open clusters, we selected sources with
quoted membership probability above 50\%.
To obtain {\it Gaia}-DR2 source identifiers for the members, we
performed a similar crossmatch as before, looking for sources within 5
arcseconds of the listed positions, and within $\pm$2 $G$-band
magnitudes of the prediction.
From 2{,}034{,}269 stars, this yielded a unique
best neighbor for 1{,}828{,}630 stars (89.9\% of the sample), and a choice
between two neighbors for 8.7\% of the remaining sample.

@@

\subsection{Moving groups and stellar associations}
\label{subsec:mg}

@@

We obtained Gaia DR2 identifiers from the results of the following
studies:
\citet{gagne_banyan_XI_2018},
\citet{gagne_banyan_XII_2018},
\citet{gagne_banyan_XIII_2018},
\citet{kraus_tucanahor_2014},
\citet{roser_deep_2011}, % OC, not MG...
\citet{bell_32ori_2017},
\citet{rizzuto_multidimensional_2011},
and \citet{oh_comoving_2017}, The methods applied in these studies
vary from kinematic analyses, to astrometric analyses included
Gaia-DR1 parallaxes, to photometric searches for infrared excesses, to
spectroscopic studies including RVs, H$\alpha$
emission, and Li absorption.

@@

Finally, \citet{oh_comoving_2017} searched for comoving stars in the
$\approx$2 million stars that overlapped between Tycho-2 and {\it
Gaia}-DR1.  They found many wide binaries, and also identified a large
number of comoving groups.  We chose the 2{,}134 stars that they
reported were in groups with sizes of at least 3 stars.  Using their
{\it Gaia}-DR1 source identifiers, we matched against the {\it Gaia}
archive's \texttt{dr1\_neighbourhood} table, which gave 1{,}881
nearest-neigbor stars in groups of at least three stars
\citep{marrese_gaia_2019}.

@@

After collecting the results of all the studies described above, we
merged them into a single table. We queried the
\texttt{gaiadr2.gaia\_source} table to retrieve their photometric $G$,
$G_{\rm R_p}$, and $G_{\rm B_p}$ magnitudes, as well as their
five astrometric parameters $(\alpha, \delta, \mu_\alpha, \mu_\delta,
\pi)$.
We then imposed that $G_{\rm R_p} < 16$.
The concatenated results are given in Table~N.

All told, there are 1{,}308{,}706 unique stars, from 12 distinct
membership catalogs.
Stars that are reported in multiple catalogs have their reference
information from each available catalog concatenated.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.3\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    {\bf Pipeline.} This is what we do.
		\label{fig:pipeline}
	}
\end{figure}

@@

We reduced the TESS images to lightcurves by performing a sequence of
steps using stand-alone programs.  A conceptual overview of our
pipeline is given in Figure~\ref{fig:pipeline}.  
Our overall method is in the spirit of the reduction approaches used
by \citet{Pal_2009}, \citet{soares-furtado_image_2017} and
\citet{oelkers_precision_2018}.

We begin with the calibrated full frame images produced by SPOC
(\S~\ref{subsec:observations}).  We then perform a collection of
preparatory steps, including source extraction of bright stars,
astrometric calibration, and coarse simple aperture
photometry (\S~\ref{subsec:preparation}).  Using the shape values from
the initial astrometry, we select an astrometric reference frame to
which we transform all of the calibrated images.  We construct a
photometric reference by stacking a collection of frames, and then
convolve all the transformed frames to the photometric reference, and
subtract (\S~\ref{subsec:imagesubtraction}).  We perform aperture
photometry on the subtracted images using positions projected onto the
frame from Gaia DR2.  We detrend the resulting lightcurves
(\S~\ref{subsec:lcdetrending}).  We then select stars that we believe
are ``cluster members'', roughly X\% of the overall dataset
(\S~\ref{sec:starselection}).  Focusing on the lightcurves of these
stars, their white noise and red noise properties, and point out a few
interesting cases of variability (\S~\ref{sec:results}).

@@

The TESS spacecraft began science operations on July 25, 2018.  To
keep its cameras pointed opposite the Sun, the spacecraft advances by
$\approx$$28$ degrees in ecliptic longitude every lunar month.  Data
acquired throughout each ``sector'' are downlinked at spacecraft
perigee through the Deep Space Network.  Verbose descriptions of the
spacecraft's design and operations are given by
\citet{ricker_transiting_2015} and the instrument handbook
\citep{vanderspek_2018}.

For us, the main data product of interest is the calibrated full frame
image (FFI).  Each TESS camera reads out every 2 seconds.  To produce
a manageable telemetric load, the resulting pixel values are averaged
by the onboard computer into 30 minute exposures. An on-board cosmic
ray mitigation algorithm is applied (CITE: BERTA-THOMPSON). Once
transmitted to the ground, the raw images are calibrated by the
Science Processing Operations Center.  The calibration process
includes an overscan, bias, and dark current correction, and also
divides out a flat field.  The details are given by
\citet{clarke_kepler_2017}, and the resulting science data products
are described by \citet{tess_data_product_description_2018}.

@@

\subsection{Image Preparation \& Background Removal}
\label{subsec:preparation}

@@

We then estimate the background of each frame.  We do this by
temporarily masking out pixels more than $2\sigma$ from the median,
and then passing a $48\times48$ median box filter over each pixel in
the image, using reflective boundary conditions. We subtract out this
smooth background estimate from each image.  This step helps mitigate
two unwanted image artifacts.  First, it removes a low-level glow
present in the corners of many images, which remains even after
flat-fielding \citep[see][\S 7.3.5]{vanderspek_2018}.  Second,
background subtraction removes scattered light patches from the Earth
and Moon, which vary in positions around the camera boresight over
each spacecraft orbit \citep[see][\S 7.3.1--7.3.4]{vanderspek_2018}.
The typical size of scattered light patches is greater than 48 pixels,
and their typical amplitude is $\sim 10\times$ the sky background
level.

% We found this background subtraction step to be particularly important
% in our subsequent difference imaging analysis. In its absense, the
% scattered light artifacts could introduce erroneous residuals into the
% kernel solution used to match reference and target images.  Including
% this step mitigated such effects, and helped produce clean
% subtractions.  Even after subtraction, a small fraction of frames also
% show sharp features (caustics) below our median box filter's size
% scale.  Such features may affect flux measurements at specific times
% in a small subset of lightcurves.

After subtracting the background, we mask out saturated stars using a
fixed saturation level of $8\times10^4\,{\rm ADU}$. This value was
chosen based on the onset of visible trails of bleeding charge, and is
slightly greater than the expected saturation level quoted by
\citet{vanderspek_2018}.  As described by \citet{Pal_2009}, our masks
are metadata to the image, and are only applied to the
pixel values during the specific image processing steps ({\it e.g.},
convolution) in which they are necessary. We also extend the masks
beyond purely saturated pixels to ``bloomed'' pixels horizontally and
vertically adjacent to the saturated pixels using the algorithm
described by \citet{Pal_2009}.

Finally, for frames with the \texttt{DQUALITY} bit-flag corresponding
to the ``momentum dumps'' and ``coarse pointing modes'' described by
\citet{vanderspek_2018}, we mask out the entire frame.  This removes
on average a few frames per sector. Through visual inspection, we see
that the stars on these frames are extremely smeared, and are unlikely
to produce useful science data.
In addition, we use the sector-specific data release
notes\footnote{\url{ archive.stsci.edu/tess/tess_drn.html}} to
identify further  times with anomalously poor spacecraft performance,
which we omit from consideration. For Sectors 1 through 5, these
include coarse pointing windows from orbits 10, 13, 14, and an
instrumetal anomaly window in orbit 15.

Next, we perform some initial analysis steps to produce metadata
needed during image subtraction.  To obtain an astrometric solution
(independent from the WCS data packaged with the frames), we use
\texttt{fistar} to perform source extraction on bright stars in each
image.  We pass the resulting source lists through
\texttt{astrometry.net} \citep{lang_2010}, which returns an
astrometric solution for each frame packaged in the WCS format
\citep[][Sec.~8]{pence_fits_2010}.  During the initial source
extraction, we also fit elongated gaussians to the bright stars,
yielding the shape parameters $(s,d,k)$, where the flux as a function
of position is assumed to take the form
\begin{align}
  f_{\rm elong}(\vec{x}) &= B + A \exp \{ -0.5 \times ( 
    s(\Delta x^2 + \Delta y^2) + \\
    \nonumber
    &d(\Delta x^2 - \Delta y^2) +
    k(2\Delta x \Delta y)
  )  \},
\end{align}
for $\Delta x = x-x_0$, and $\Delta y = y - y_0$.  For a nearly
circular shape profile, the sharpness $s$ is related to the FWHM as
${\rm FWHM} \approx 2.35\sqrt{s}$ \citep[{\it e.g.},][]{Pal_2009}.
These shape parameters are later used when selecting an astrometric
reference (\S~\ref{subsec:imagesubtraction}).  We note that the fast
focal ratio of the TESS cameras introduces significant comatic
aberrations to the images: stars closer to the center of the field are
more round, while stars towards the edges are more triangular.

With the resulting WCS information, we then project a source catalog
from Gaia-DR2 onto the frame, down to a pre-selected magnitude cutoff
\citep{gaia_collaboration_gaia_2018}.  We use these expected positions
to center the apertures in our photometry, rather than attempting to
detect the positions.  Such ``forced-aperture photometry'' is
preferable to performing source extraction because of the large TESS
pixels, and the accurate Gaia positions.  The Gaia-DR2 epoch is
J2015.5, so even the fastest-moving stars with proper motions of
$\sim$$1\,{\rm arcsecond}\,{\rm yr}^{-1}$ are still well within one pixel
of their predicted positions in the TESS images.  The projection and
catalog-indexing is performed using
\texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
\citep{kim_2018_gaia2read}.

Finally, we perform aperture photometry on the bright stars from the
source list, by summing the counts inside appropriately-weighted
circular apertures centered on the projected positions from Gaia DR2. 
The pixel weights $w_{x,y}$ are equal to the fraction of the pixel
that falls within the aperture.  They are thus unity for pixels
entirely within the aperture, and fractional along the aperture
boundary (e.g., \citealt{Pal_2009} Fig 17). 
The background levels are measured in annuli around each aperture
center.  The raw flux of the object after background removal is then
(\citealt{Pal_2009} Eq 65)
\begin{equation}
  f = \sum_{x,y} w_{x,y} (I_{x,y} - B) = f_{\rm total} - B r_0^2.
  \label{eq:simple_aperture_phot}
\end{equation}
The resulting measurements, for instance of the background level of
each aperture, and the number of ``good'' objects that are detected,
are later used as input for selecting photometric reference frames.

@@

\item {\it Centroid positions vs. time}.  The main variability in the
  centroid positions as a function of time is a secular drift, that is
    reset every orbit.  The 2.5 day momentum wheel dump is
    superimposed on this secular drift, and has smaller amplitude than
    the drift.

>>>>

\shortauthors{Bouma et al.}
\shorttitle{CDIPS I: Method \& Sectors 6--8}

@@

\title{
  The Cluster Difference Imaging Photometric Survey (CDIPS).
  I. Method, Light Curves, and Planet Candidates from Sectors 6--8
}

@@

The exoplanet field is evolving.
At the beginning, Doppler spectroscopy by the Geneva and California groups
led to the first exoplanet detections (CITE: Mayor 95, Butler, Marcy).
Some of these planets transited (CITE: Henry, Charbonneau).
Despite the geometric rarity of transits, photometric monitoring can
be performed in parallel; with precise spectroscopy this has not
yet been achieved.
Parallel photometric monitoring enabled thousands of planet detections
with the Kepler spacecraft (CITE: Borucki, Morton).
The abundance of planets from Kepler taught us about statistics
(CITE: Howard, Fressin, Petigura).
By nature of its design, Kepler left open two major avenues for
improvement: (i) brighter stars, (ii) rare weirdos.
TESS (CITE: Ricker), by nature of its small, wide-field cameras, and
nearly all-sky coverage, can capitalize on both.

One class of rare weirdo to which TESS is sensitive is stars in
clusters.  For brevity, we use the term ``cluster'' to refer to open
clusters, moving groups, associations, and star-forming regions.
Each of the $\sim$1000 star clusters of the Milky Way is a gift to
astrophysics, providing a sample of stars that vary widely in mass
but all have approximately the same age and composition.

Cluster stars have been photometered from the ground for a while
(CITE: Joel thesis, Cambridge group).
A few clusters, NAME1 and NAME2, were observed by Kepler in its prime
mission (CITE: Meibom).
And a few more, most notably X,Y, and Z, were observed in K2's
ecliptic mission (CITE).

@@

However, there are formidable obstacles to deriving precise photometry
from the {\it TESS} images because of the relatively poor angular
resolution.  Almost all of the clusters are within 10 degrees of the
Galactic plane (see Figure~1), where the problems with crowding and
complex backgrounds are so severe that the {\it TESS}\, Science Team
has neglected that portion of the sky in their planet simulations
\citep{Sullivan_et_al_2015}. Similarly, the {\it TESS}\, Candidate
Target List deprioritizes all objects within $15^\circ$ of the
galactic plane~\citep{stassun_TIC_2018}, which includes 90\% of all
star clusters.  The large pixel size and the high stellar surface
density will make aperture photometry unreliable.  Yet, aperture
photometry is the basis of the official {\it TESS} data reduction
pipeline and almost all reduction methods that have been applied to
{\it Kepler} and {\it K2} data.

We have begun to produce photometry from the TESS images.
For the time being, we are adopting the difference imaging (or
optionally, ``image subtraction'') technique, because of its
benefits in modelling complex backgrouds in crowded regions.

In what follows, \S~\ref{sec:method} presents BLAH, and
\S~\ref{sec:results} describes BLAH BLAH.
\S~\ref{sec:discussion} discusses, and \S~\ref{sec:conclusion}
concludes.

@@

A major motivator for the CDIPS project is to increase the number of
cluster stars for which continuous photometric timeseries are
available, and thus facilitate studies of exoplanetary and stellar
processes across different times and stellar environments.
An essential aspect of the project is therefore to define a {\it
cluster star sample}, made of stars that are thought to be
members of clusters.

Performing a homogeneous membership determination for every known
cluster is beyond the scope of the current work.  Instead, we collect
various cluster membership catalogs from the literature.  We then use
them to identify cluster members within the TESS images.  In initially
selecting stars, we aim for completeness, not accuracy.  If there has
been a claim in the literature that a star should be considered a
cluster member, we would like to report a light curve for the star.
For stars that are photometrically interesting, we can perform post-hoc
cluster membership quality checks using Gaia DR2 astrometry and photometry.

Table~N describes the cluster membership catalogs we have used to
identify candidate cluster members.  Since our photometric reduction
is based on positions reported in {\it Gaia DR2}, each of our
light curve sources by default is associated with a Gaia identifier.
Correspondingly, the cluster membership determinations performed by
\citet{cantat-gaudin_gaia_2018} and \citet{gaia_hr_2018} are the
easiest case for us to merge against our light curve database.
For the TESS Sectors 1--5 light curves produced in this study, this
yielded X and Y light curves respectively.

@@

\subsection{Big catalogs: open clusters}
\label{subsec:oc}

@@

\citet{cantat-gaudin_gaia_2018} used an unsupervised membership
assignment algorithm to identify clusters in the three-dimensional
astrometric space of proper motion and parallax. They used {\it Gaia}
photometry and radial velocities to then verify the claimed
membership properties.  From their Table~2, we collect an initial 401{,}448
cluster members, in 1229 clusters, down to their limiting magnitude of
$G=18$.

@@

\paragraph{Pre-{\it Gaia} OC memberships}
\citet{Kharchenko_et_al_2013} used proper motions calculated in PPMXL
\citep[][a combination of USNO-B1{.}0 and 2MASS
astrometry]{roeser_ppmxl_2010} and near-infrared photometry from 2MASS
\citep{skrutskie_tmass_2006} to report the existence of 2859 open
clusters and stellar associations.
We selected their ``$1\sigma$'' members according to the
combined photometric, kinematic, and spatial criteria described by
\citet{kharchenko_global_2012}.  Then, to obtain {\it Gaia}-DR2 source
identifiers for the members, we performed a crossmatch for {\it
Gaia}-DR2 sources within 5 arcseconds of the listed positions.  As an
additional constraint, we used the 2MASS photometry to predict the
$G$-band magnitudes\footnote{See
\url{https://gea.esac.esa.int/archive/documentation/GDR2/Data_processing/chap_cu5pho/sec_cu5pho_calibr/ssec_cu5pho_PhotTransf.html},
online, \texttt{2019-03-29}, or \citet{carrasco_gaia_2016}}, and
required that the measured $G$-magnitude fall within 2 magnitudes of
the predicted $G$-magnitude.  If multiple neighbors matched the
position and magnitude constraints, we took the nearest spatial
neighbor as the match.  From 373{,}226 stars, this yielded a unique
best neighbor for 352{,}332 stars (94.4\% of the sample), and a choice
between two neighbors for 17{,}774 stars.

%FIXME is this it?
The second (non-{\it Gaia} derived) open cluster membership catalog we
used was the \citet{dias_proper_2014} catalog, which was based on
UCAC4 proper motions.
From their 1805 reported open clusters, we selected sources with
quoted membership probability above 50\%.
To obtain {\it Gaia}-DR2 source identifiers for the members, we
performed a similar crossmatch as before, looking for sources within 5
arcseconds of the listed positions, and within $\pm$2 $G$-band
magnitudes of the prediction.
From 2{,}034{,}269 stars, this yielded a unique
best neighbor for 1{,}828{,}630 stars (89.9\% of the sample), and a choice
between two neighbors for 8.7\% of the remaining sample.

@@

\subsection{Smaller catalogs: moving groups and stellar associations}
\label{subsec:mg}

@@

We obtained Gaia DR2 identifiers from the results of the following
studies:
\citet{gagne_banyan_XI_2018},
\citet{gagne_banyan_XII_2018},
\citet{gagne_banyan_XIII_2018},
\citet{kraus_tucanahor_2014},
\citet{roser_deep_2011}, % OC, not MG...
\citet{bell_32ori_2017},
\citet{rizzuto_multidimensional_2011},
\citet{oh_comoving_2017}, and
\citet{zari_3d_2018}. The methods applied in these studies
vary from kinematic analyses, to astrometric analyses included
Gaia-DR1 parallaxes, to photometric searches for infrared excesses, to
spectroscopic studies including RVs, H$\alpha$
emission, and Li absorption.

@@

Next, \citet{oh_comoving_2017} searched for comoving stars in the
$\approx$2 million stars that overlapped between Tycho-2 and {\it
Gaia}-DR1.  They found many wide binaries, and also identified a large
number of comoving groups.  We chose the 2{,}134 stars that they
reported were in groups with sizes of at least 3 stars.  Using their
{\it Gaia}-DR1 source identifiers, we matched against the {\it Gaia}
archive's \texttt{dr1\_neighbourhood} table, which gave 1{,}881
nearest-neigbor stars in groups of at least three stars
\citep{marrese_gaia_2019}.

Finally, \citet{zari_3d_2018} constructed a sample of young stars
within $500\,{\rm pc}$ using data from Gaia-DR2. Two subsamples were
made: (a) an upper main sequence (MS) sample, with 86{,}102 stars, and
(b) a pre-MS sample, with 43{,}719 stars.  Each was created from a
careful combination of distinct astrometric and photometric cuts.
These stars are the youngest, closest stars, spread across
star-forming complexes in Sco-Cen, Orion, Vela, Taurus, and other
regions of the sky.  Though many are not strictly identified with
moving groups or open clusters, their reported youth and proximity to star
forming regions justifies their inclusion in our search sample.

@@

After collecting the aforementioned lists, we
merged them into a single table. We then queried the
\texttt{gaiadr2.gaia\_source} table to retrieve their photometric $G$,
$G_{\rm Rp}$, and $G_{\rm Bp}$ magnitudes, as well as their
astrometric measurements $(\alpha, \delta, \mu_\alpha, \mu_\delta,
\pi)$.  Finally, we required that $G_{\rm Rp} < 16$.

All told, this procedure yielded 1{,}061{,}447 unique stars, from 13 distinct
membership catalogs.

107{,}647 of these stars, or about
10\% of the collection, have cluster memberships reported by
multiple authors.  The largest number of stars come from
\citealt{dias_proper_2014} (44.3\% of stars), \citealt{Kharchenko_et_al_2013}
(17.3\%), \citealt{cantat-gaudin_gaia_2018} (16.7\%), and \citealt{zari_3d_2018}
(11.1\%).
Stars reported in multiple catalogs have all available reference information
concatenated.  
The resulting CDIPS target star list is given in Table~N.

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.3\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.2cm}
	\caption{
    {\bf Conceptual overview of photometric reduction pipeline.}
    Details are given in \S~\ref{sec:method}.
	\label{fig:pipeline}
	}
\end{figure}

@@

We reduced the TESS images to light curves by performing a sequence of
steps using stand-alone programs.
Our overall method is in the spirit of the reduction approaches described
by \citet{Pal_2009}, \citet{soares-furtado_image_2017} and
\citet{oelkers_precision_2018}; a conceptual overview is given in
Figure~\ref{fig:pipeline}.

We begin with the calibrated full frame images produced by the Science
Processing Operations Center at NASA Ames (\S~\ref{subsec:observations}).
We then perform a collection of
preparatory steps, including source extraction of bright stars,
astrometric calibration, and coarse simple aperture
photometry (\S~\ref{subsec:preparation}).  Using the shape values from
the initial astrometry, we select an astrometric reference frame to
which we transform all of the calibrated images.  We construct a
photometric reference by stacking a collection of frames,
convolve the transformed frames to this photometric reference, and
subtract (\S~\ref{subsec:imagesubtraction}).  We perform aperture
photometry on the subtracted images using positions projected onto the
frame from Gaia DR2.  
We detrend the resulting light curves
(\S~\ref{subsec:lcdetrending}).  The resulting white noise and red noise properties
of the light curves, and a few
interesting cases of variability, are discussed in \S~\ref{sec:results}.

@@

The TESS spacecraft began science operations on July 25, 2018.  To
keep its cameras pointed opposite the Sun, the spacecraft advances by
$\approx$$28$ degrees east in ecliptic longitude every lunar month.  Data
acquired throughout each ``sector'' are downlinked at spacecraft
perigee through the Deep Space Network.  Verbose descriptions of the
spacecraft's design and operations are given by
\citet{ricker_transiting_2015} and the instrument handbook
\citep{vanderspek_2018}.

For us, the main data product of interest is the calibrated full frame
image (FFI).  Each TESS camera is read out every 2 seconds.  To produce
a manageable telemetric load, the resulting pixel values are averaged
by the onboard computer into 30 minute exposures. An on-board cosmic
ray mitigation algorithm is applied (CITE: BERTA-THOMPSON). Once
transmitted to the ground, the raw images are calibrated by the
Science Processing Operations Center.  The calibration process
includes an overscan, bias, and dark current correction, and also
divides out a flat field.  Details are discussed by
\citet{clarke_kepler_2017}, and the resulting science data products
are described by \citet{tess_data_product_description_2018}.

@@

While we performed numerous initial tests on the first sectors of data,
by geometric coincidence Sectors 1--5 fell away from the galactic plane.
Less than 2\% of the CDIPS target star sample
is therefore observed in the first five TESS sectors.
Though a few interesting clusters are present ({\it e.g.}, Blanco~1, NGC~2516, NGC~1901),
for the time being we opted to focus on sectors in which there were stars
of interest for our intended science.
These begin in Sector 6 (2018-12-12, spacecraft orbit \#19).

\subsection{Image Preparation, Background Removal, \& Meta-Data Collection}
\label{subsec:preparation}

@@

In order to pre-emptively address the background
variations present in some frames due to scattered light from the
Earth and Moon \citep[see][\S 7.3.1--7.3.4]{vanderspek_2018},
we then estimate and subtract the large-scale background.
We do this by
temporarily masking out pixels more than $2\sigma$ from the image median,
and then pass a $48\times48$ median box filter over each pixel in
the image, with reflective boundary conditions. 
We blur the resulting background estimate with a gaussian kernel,
which produces a
smooth background estimate for each image.  These steps also remove
a low-level vignetting
present in the corners of many images, which remains even after
flat-fielding \citep[see][\S 7.3.5]{vanderspek_2018}.
With the exception of scattered-light caustics, which remain in small
areas of less than 10\% of the frames, this ad-hoc procedure removes
large spatial scale scattered light patches.

% We found this background subtraction step to be particularly important
% in our subsequent difference imaging analysis. In its absense, the
% scattered light artifacts could introduce erroneous residuals into the
% kernel solution used to match reference and target images.  Including
% this step mitigated such effects, and helped produce clean
% subtractions.  Even after subtraction, a small fraction of frames also
% show sharp features (caustics) below our median box filter's size
% scale.  Such features may affect flux measurements at specific times
% in a small subset of light curves.

After subtracting the background, we mask out saturated stars using a
fixed saturation level of $8\times10^4\,{\rm ADU}$. This value was
chosen based on the onset of visible trails of bleeding charge, and is
slightly greater than the expected saturation level quoted by
\citet{vanderspek_2018}.  As described by \citet{Pal_2009}, our masks
are metadata to the image, and are only applied to the
pixel values during the specific image processing steps in which they
are necessary ({\it e.g.}, convolution). We also extend the masks
beyond purely saturated pixels to ``bloomed'' pixels horizontally and
vertically adjacent to the saturated pixels (see Figure~6 of \citealt{Pal_2009}).

Finally, for frames with the \texttt{DQUALITY} bit-flag corresponding
to the ``momentum dumps'' and ``coarse pointing modes'' described by
\citet{vanderspek_2018}, we omit the entire frame.  This removes
on average a few frames per sector. Through visual inspection, we see
that the stars on these frames are extremely smeared, and are unlikely
to produce useful science data.
In addition, we use the sector-specific data release
notes\footnote{\url{ archive.stsci.edu/tess/tess_drn.html}} to
identify further times with anomalous spacecraft performance,
which we omit from consideration.
%For Sectors 1 through 5, these
%include coarse pointing windows from orbits 10, 13, 14, and an
%instrumetal anomaly window in orbit 15.
For Sectors 6 through 8, these include three days at the beginning of
Sector 6 dedicated to acquiring pixel response function data, and also
about three days during Sector 8 lost to an instrument anomaly.
%FIXME for sectors 6 thru 8

Having prepared the images, we perform some initial analysis steps
to produce metadata
needed during image subtraction.  To obtain an astrometric solution
(independent from the solution included with the frames), we use
\texttt{fistar} to perform source extraction on bright stars in each
image.  We pass the resulting source lists through
\texttt{astrometry.net} \citep{lang_2010}, which returns an
astrometric solution for each frame packaged in the WCS format
\citep[][Sec.~8]{pence_fits_2010}.  During the initial source
extraction, we also fit elongated gaussians to the bright stars,
yielding the shape parameters $(s,d,k)$, where the flux as a function
of position is assumed to take the form
\begin{align}
  f_{\rm elong}(\vec{x}) &= B + A \exp \{ -0.5 \times ( 
    s(\Delta x^2 + \Delta y^2) + \\
    \nonumber
    &d(\Delta x^2 - \Delta y^2) +
    k(2\Delta x \Delta y)
  )  \},
\end{align}
for $\Delta x = x-x_0$, and $\Delta y = y - y_0$.  For a nearly
circular shape profile, the sharpness $s$ is related to the FWHM as
${\rm FWHM} \approx 2.35\sqrt{s}$ \citep[{\it e.g.},][]{Pal_2009}.
These shape parameters are later used when selecting an astrometric
reference (\S~\ref{subsec:imagesubtraction}).  We note that the fast
focal ratio of the TESS cameras introduces significant comatic
aberrations to the images: stars closer to the center of the field are
more round, while stars towards the edges are more triangular.

With the resulting WCS information, we then project a source catalog
onto each frame.
Initially, we intended to photometer all Gaia-DR2 sources in each field
down to a cutoff of $G_{Rp} < 16$.
However, we found that for the galactic plane fields this produces an
excessively large number of sources.
Our source catalog for each frame is therefore a combination of
the CDIPS target stars ($G_{Rp} < 16$), and all Gaia-DR2 sources down to
$G_{Rp} < 13$.
We use the expected positions of these sources
to center the apertures in our photometry, rather than attempting to
detect the positions.  Such ``forced-aperture photometry'' is
preferable to performing source extraction simply because the TESS
pixels are large, and we are operating in crowded fields.
The Gaia-DR2 epoch is
J2015.5, so even the fastest-moving stars with proper motions of
$\sim$$1\,{\rm arcsecond}\,{\rm yr}^{-1}$ are still well within one pixel
of their predicted positions in the TESS images.  The projection from
catalog sky-coordinate positions to pixel coordinates
is performed using standard WCS transformations, 
and the source catalog look-up is
performed using
\texttt{gaia2read}\footnote{\url{github.com/samuelyeewl/gaia2read}}
\citep{kim_2018_gaia2read}.

Finally, we use \texttt{fiphot} to perform aperture photometry on the
bright stars from the
source list, by summing the counts inside appropriately-weighted
circular apertures centered on the projected positions from Gaia DR2. 
The pixel weights $w_{x,y}$ are equal to the fraction of the pixel
that falls within the aperture.  They are thus unity for pixels
entirely within the aperture, and fractional along the aperture
boundary (see \citealt{Pal_2009} Fig 17). 
The background levels are measured in annuli around each aperture
center.  The raw flux of the object after background removal is then
(\citealt{Pal_2009} Eq 65)
\begin{equation}
  f = \sum_{x,y} w_{x,y} (I_{x,y} - B) = f_{\rm total} - B r_0^2.
  \label{eq:simple_aperture_phot}
\end{equation}
The resulting measurements, for instance of the background level of
each aperture, and the number of ``good'' objects that are detected,
are later used as input for selecting photometric reference frames.

@@

\item {\it Centroid positions vs\ time}.  The main variability in the
  centroid positions as a function of time is a secular drift, that is
    reset every orbit.  The 2.5 day momentum wheel dump is
    superimposed on this secular drift, and has smaller amplitude than
    the drift.
